Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
added transition from sec:prev to sec:data

We argue, however, that it is possible to significantly improve the performance
of the downstream application of syntactic parsing by introducing
linguistically informed, syntactically informative distinctions in a tag set.
We will now turn to the data that provided the basis for our experiments and
outline its morphological and syntactic annotation choices.

>>>>

We argue, however, that it is possible to significantly improve the performance
of the downstream application of syntactic parsing by introducing
linguistically informed, syntactically informative distinctions to a tag set.
We will now turn to the data that provided the basis for our experiments and
outline its morphological and syntactic annotation choices.
